Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*

### 2024-02-06 Code/Manuscript_O2.Rmd
Generated combined blue and red GAMs

library(lubridate)
library(broom)
library(knitr)
library(grid)
library(bookdown)
library(glue)
library(cowplot)
library(ggpubr)
# library(RColorBrewer)
library(tidyverse)

@@

# Results {.unnumbered}

%%%% Insert OceanDepthO2ProteinPhotosynth figure from OceanPortal repository  %%%

@@

>>>>

library(lubridate)
library(broom)
library(knitr)
library(grid)
library(bookdown)
library(glue)
library(cowplot)
library(ggpubr)
# library(RColorBrewer)
library(tidyverse)
library(png)
library(cowplot)

@@

# Results and Discussion {.unnumbered}

%%%% OceanProteinPortal data show complexes in environment  %%%

@@

```{r MED4GAM,  fig.cap = MED4GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}

MED4GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.  The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmole photons m-2 s-1) **",
                       "Rows are...",
                       "Columns are...",

knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MED4_Oxy_.png"))
